Pillar 1 - Sequential Pattern Mining

### 2019-01-21 Pillar 1 - Sequential Pattern Mining.Rmd

@@

```{r}
rules <- ruleInduction(frequent_trajectories, confidence = 0.2, #we need to play with the parameters.
                    control    = list(verbose = TRUE))
as(rules, "data.frame") %>%
  arrange(desc(lift))
```
#Sequence mining with pass fail.
First we add pass fai information to our data set and transform it to transactions class:
```{r}
#sequences
fail_threshold <- 6.5

>>>>

#checking results
as(my_transactions, "data.frame")
```

@@

```{r}
rules <- ruleInduction(frequent_trajectories, confidence = 0.2, #we need to play with the parameters.
                    control    = list(verbose = TRUE))
as(rules, "data.frame") %>%
  arrange(desc(lift))
```
#Sequence mining with pass fail.
First we add pass fail information to our data set and transform it to transactions class:
```{r}
#sequences
fail_threshold <- 6.5
